\documentclass[10pt]{article}
\usepackage{refcount}
\usepackage{charter}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage[resetlabels]{multibib}
\usepackage[ManyBibs,LabelsAligned]{currvita}
\usepackage{ifpdf}
\usepackage{denselists}
%\usepackage{revnum}

\ifpdf
  \usepackage[pdftex,pdfpagelabels=false]{hyperref}
\else
  \usepackage[hypertex,pdfpagelabels=false]{hyperref}
\fi
\usepackage{setspace} 
\hypersetup{
  pdfauthor={Jason E Stajich}
  pdftitle={CV for Jason Stajich}
  pdfsubject={Detailed CV for Jason},
  urlcolor=blue,
}

% Initialize each paper type for which you need a bibliography.
% Just a dummy parameter is necessary.
\newcites{journal}{nih}
%\newcites{submitpaper}{foo}
\newcites{book}{nih}
\newcites{review}{nih}
\newcites{report}{nih}
\newcites{essay}{nih}
\newcites{commentary}{nih}

\usepackage{etaremune}
\makeatletter
\long\def\thebibliography#1{%
  \section*{\refname}%
  \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}
  \settowidth{\dimen0}{\@biblabel{#1}}%
  \setlength{\dimen2}{\dimen0}%
  \addtolength{\dimen2}{\labelsep}
  \sloppy
  \clubpenalty 4000 
  \@clubpenalty 
  \clubpenalty 
  \widowpenalty 4000
  \sfcode `\.\@m
  \renewcommand{\labelenumi}{\@biblabel{\theenumi}} % labels like [3], [2], [1]
  \begin{etaremune}[labelwidth=\dimen0,leftmargin=\dimen2]\@openbib@code
}
\def\endthebibliography{\end{etaremune}}
\def\@bibitem#1{%
  \item \if@filesw\immediate\write\@auxout{\string\bibcite{#1}{\the\value{enumi}}}\fi\ignorespaces
}
\makeatother

\begin{document}

% Specify the bibtex style that you want for each paper type
\bibliographystyle{nih}
%\bibliographystylesubmitpaper{nih}
\bibliographystylejournal{nih}
\bibliographystylereview{nih}
\bibliographystylebook{nih}
\bibliographystylereport{nih}
\bibliographystylecommentary{nih}
\bibliographystyleessay{nih}

% We'll use this length to change the defaults in some of our lists.
\newlength{\oldcvlabelwidth}
\renewcommand*{\cvbibname}{}

% This is what will appear at the very top of your CV.
\begin{cv}{\centerline{Jason E. Stajich}}

% Items have more vertical space between them than line breaks.
% Note: if you want a linebreak after each cvlist title, you can do:
% \begin{cvlist}{Title \hspace{3in}}

\setlength{\cvlabelwidth}{18mm}
\begin{cvlistcompact}{Contact}
\item{Department of Plant Pathology \& Microbiology, Institute for
  Integrative Genome Biology, \\
  University of California, Riverside, CA 92521}
  \item{ \textbf{Telephone:} +1 951-827-2363 \textbf{Email:}
    jason.stajich@ucr.edu \\
    \textbf{Web:} \url{http://lab.stajich.org/} {\tt @stajichlab @hyphaltip}}
\end{cvlistcompact}

\begin{cvlistcompact}{\bf Education}
\item [2006--2009] Postdoctoral training, University of California, Berkeley, CA. Mentor: Dr. John W Taylor
\item [2001--2006] Ph.D. in Genetics and Genomics, Duke University, Durham, NC. Advisor: Dr. Fred S Dietrich
\item [1995--1999] B.S. in Computer Science, Duke University, Durham, NC
\end{cvlistcompact}

\begin{cvlistcompact}{\bf Academic appointments:}
\item [2014--] Associate Professor (with tenure)
  \\ Dept of Plant Pathology \& Microbiology. University of California Riverside
\item [2009--2014] Assistant Professor
  \\ Dept of Plant Pathology \& Microbiology. University of California Riverside.
\item [2006--2009] Postdoctoral Research Fellow. Miller Institute for Basic Research. \\
  Dept of Plant and Microbial Biology, University of California
  Berkeley. \\
\end{cvlistcompact}

\begin{cvlistcompact}{Honors and Awards:}
\item [2015] Kavli Fellow, Kavli Frontiers of Science
\item [2014] C. J. Alexopoulos Prize, Mycological Society for America
\item [2006--2009] Miller Institute for Basic Research in Science,
  Postdoctoral Research Fellowship
\item [2003--2006] National Science Foundation, Graduate Research Fellowship
\end{cvlistcompact}

% These commands will make our papers be indented after the first line
% to make the author's name stand out more.  Also, we reduce the
% indentation of the paper type titles (e.g., Journal Papers,
% Conference Paper) compared to regular cvlist items.
\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\renewcommand*{\bibindent}{1.5em}
% Do bibaddtoleftmargin instead of biblabelsep if you're
% not using manybib Or open bib
%\renewcommand*{\bibaddtoleftmargin}{1.5em}
\renewcommand*{\biblabelsep}{1.5em}

% To update, before doing latexmk, run:
% bibtex journal
% bibtex refpaper
% bibtex unrefpaper
% bibtex techreport
\begin{cvlist}{Publications: (Listed in reverse chronological order.)}
  % With multibib, each cite command has the type after it.
  \item \textbf{Peer Reviewed Publications}

\makeatletter
\def\thebibliography#1{\list
{\arabic{enumiv}.}{\settowidth\labelwidth{[#1]}\leftmargin\labelwidth
\advance\leftmargin\labelsep
\usecounter{enumiv}}
\def\newblock{\hskip .11em plus .33em minus .07em}
\sloppy\clubpenalty4000\widowpenalty4000
\sfcode`\.=1000\relax
}
\let\endthebibliography=\endlist
\makeatother


\def\mybibitem#1{\item}

\nocitejournal{Nguyen2016}
\nocitejournal{Torres-Cruz2016}
 \nocitejournal{Ahrendt2016}
 \nocitejournal{Chen2016}
 \nocitejournal{Cisse2016}
  \nocitejournal{Short2016}
  \nocitejournal{Spatafora2016}
  \nocitejournal{Castanera2016}
  \nocitejournal{Lee2016}
  \nocitejournal{deMan2016}
  \nocitejournal{URen2016}
  \nocitejournal{Pieuchot2015}
  \nocitejournal{Wang2015}
  \nocitejournal{Liu2015}
  \nocitejournal{Willger2015}
  \nocitejournal{Collins2015}
  \nocitejournal{Melida2015}
  \nocitejournal{Teixeira2014}
  \nocitejournal{Ouyang2014}
  \nocitejournal{Inglis2014}
  \nocitejournal{Treseder2014}
  \nocitejournal{Janbon2014}
  \nocitejournal{Sachs2014}
  \nocitejournal{Traeger2013}
  \nocitejournal{Gryganskyi2013}
  \nocitejournal{Gioti2013b}
  \nocitejournal{James2013}
  \nocitejournal{Rosenblum2013}
  \nocitejournal{Robb2013}
  \nocitejournal{Jamieson2013}
  \nocitejournal{Cheng2013}
  \nocitejournal{Gioti2013a}
  \nocitejournal{Nygren2012}
  \nocitejournal{Abramyan2012}
  \nocitejournal{Gioti2012}
  \nocitejournal{Stajich2012}
  \nocitejournal{Joneson2011}
  \nocitejournal{Ellison2011}
  \nocitejournal{DSouza2011}
  \nocitejournal{Burns2010}
  \nocitejournal{Smith2010}
  \nocitejournal{Levesque2010}
  \nocitejournal{Strandberg2010}
  \nocitejournal{Ohm2010}
  \nocitejournal{Stajich2010}
  \nocitejournal{Neafsey2010}
  \nocitejournal{Nowrousian2010}
  \nocitejournal{Sharpton2009}
  \nocitejournal{Fisher2009}
  \nocitejournal{Rosenblum2008}
  \nocitejournal{Regier2008}
  \nocitejournal{Martin2008}
  \nocitejournal{Lilly2008}
  \nocitejournal{Hu2008}
  \nocitejournal{Stajich2007a}
  \nocitejournal{Fraser2007}
  \nocitejournal{Harrison2007}
  \nocitejournal{Erwin2007}
  \nocitejournal{Fitzpatrick2006}
  \nocitejournal{Demuth2006}
  \nocitejournal{James2006}
  \nocitejournal{Kaemper2006}
  \nocitejournal{Stajich2006a}
  \nocitejournal{Giles2006}
  \nocitejournal{Cramer2006}
  \nocitejournal{Hesselberth2006}
  \nocitejournal{Stajich2005}
  \nocitejournal{Mitreva2005}
  \nocitejournal{Leman2005}
  \nocitejournal{Hahn2005}
  \nocitejournal{Fraser2005}
  \nocitejournal{Kraus2004}
  \nocitejournal{Stein2003}
  \nocitejournal{Hahn2003}
  \nocitejournal{Stein2002}
  \nocitejournal{Stajich2002}
  \nocitejournal{Baxter2002}
  

%  \nocitejournal{Lu2014}
%  \nocitejournal{Sain2014}


  \bibliographyjournal{stajichpubs}

\item \textbf{Reviews (Refereeed)}
  \nocitereview{Hibbett2013}
  \nocitereview{Rosenblum2010}
  \nocitereview{Rosenblum2010a}
  \nocitereview{Stajich2009a}
  \nocitereview{Stajich2006}
  \bibliographyreview{stajichpubs}

  \item \textbf{Books and Book Chapters} 
  \nocitebook{Stajich2015}  
  \nocitebook{Stajich2013}  
  \nocitebook{Fisher2012}
  \nocitebook{McKay2010}
  \nocitebook{Edwards2009}
  \nocitebook{Stajich2007}
  \nocitebook{Stajich2006b}
  \nocitebook{Coghlan2006}

  \bibliographybook{stajichpubs}

\item \textbf{Meeting and Technical Reports}
  \nocitereport{Momany2015}
  \nocitereport{Kennedy2015}
  \nocitereport{Glass2014}
  \nocitereport{Bates2013}
  \nocitereport{Lapp2007}

  \bibliographyreport{stajichpubs}

\item \textbf{Commentaries and Book Reviews}
  \nocitecommentary{Stajich2016}
  \nocitecommentary{Stajich2011}
  \nocitecommentary{Stajich2009b}

  \bibliographycommentary{stajichpubs}
  
\item \textbf{Essays}
  \nociteessay{Stajich2014}
  \bibliographyessay{stajichpubs}
  
\begin{cvlistcompact}{\bf Software and other Products}
  \item BioPerl - \url{http://bioperl.org} - Core developer
\item Github \url{http://github.com/hyphaltip} - individual
  projects
\item Github \url{http://github.com/stajichlab} - lab
  projects

 \item Github \url{http://github.com/1KFG} - 1000 Fungal
   genomes project
\item Github \url{http://github.com/zygolife} - ZyGoLife NSF project
  and associated phylogenomics
\item Website: \url{http://1000.fungalgenomes.org} - 1KFG project
\item Website: \url{http://zygolife.org} - NSF Zygolife
\item Website: \url{http://dynamiterice.org} - NSF Rice Transposable
    Element project
\item Website: \url{http://fungalgenomes.org/blog} - ``The Hyphal
  Tip'' A Blog I write about Fungal Genomics
\item Website \& Database (Collaboration): \url{http://fungidb.org}
\end{cvlistcompact}


\end{cvlist}
% Reset the label indentation
\setlength{\cvlabelwidth}{24mm}

%\begin{cvlist}{Employment}
%	\item[Summer 2002] Visiting Researcher, Lincoln D Stein laboratory \\
%          Cold Spring Harbor Laboratories, Cold Spring Harbor, NY
%	\item[1999--2001] Analyst/Programmer, Center for Human
%          Genetics \\
%          Duke University Medical Center, Durham, NC          
%\end{cvlist}

\begin{cvlistcompact}{\bf Grant Support:}
\item [{\bf Ongoing support}]

\item [2011-2016] W.M. Keck Foundation. \$1M \\
''New Active Transposable Elements for Mosquito Genetics.'' \\
Role: Co-I. PI: SR Wessler (UC Riverside). Co-I: P Atkinson (UC Riverside). 

\item [2011-2017] National Science Foundation. Plant Genome -
  IOS-1027542. \$4.9M  \\
  ``CPGS: Genome-wide impact of \textit{mPing} transposition on rice phenotypic diversity.'' \\
Role: Co-I. PI: SR Wessler (UC Riverside). Co-I: T Brutnell (Danforth
Center), Q Sun (Cornell). \\
\url{http://dynamiterice.org}

\item [2014-2017] National Institutes of Health - 1-R01-GM108492-01. \$1.5M \\
``Dynamics of bacterial-fungal interactions in chronic lung infections'' \\
Role: Co-I. PI: D Hogan (Dartmouth)

\item [2015-2018] National Science Foundation. GO Life
  DEB-1441715. \$714k (\$2.5M total award) \\
``Collaborative Research: The Zygomycetes Genealogy of Life
  (ZyGoLife)- the conundrum of Kingdom Fungi'' \\
  Role: PI. Collaborative award with 3 other PIs and ~12
  collaborating labs: J Spatafora (Oregon State), TY James (U
  Michigan), R Robertson (Arizona State) \\
\url{http://zygolife.org} 

\item [2016-2019] National Science Foundation. DEB-1557110. \$317k
  (\$709k total award) \\
``Collaborative Research: Phylogenomics and evolutionary history of the anaerobic fungal group, Neocallimastigomycota'' \\
Role: PI. Collaborative award with PI: Noha Youssef and Mostafa Elshahed (Oklahoma State)
 
\item [{\bf Completed support}]

\item [2010-2013] Burroughs Wellcome Fund. \$500k \\
 ``FungiDB: A Pan Fungal Genome Database''. \\
Role: Co-I. PI: DS Roos (U Pennsylvania)

\item [2011-2012] UC Riverside, Chancellor's Strategic Investment
  Funds. \$25k \\
``Coelomomyces Genomics for Mosquito Vector Control'' \\
Role: Co-I. PI: B Federici. Co-I: A Ray (UC Riverside)

\item [2013-2014] UC Riverside, Office of Research Strategic Investment
  Funds. \$50k \\
``High-throughput synthetic biology for natural products discovery'' \\
Role: Co-I. PI: K Borkovich. Co-I: C Larive (UC Riverside)

\item [2013-2014] National Institutes of Health - 1-R03-AI105636-01. \$168k \\
``Annotation of \textit{Cryptococcus} genomes by comprehensive
  curation of published literature'' \\
Role: PI. Co-I G Sherlock (Stanford)

  \item [2011-2014] Alfred P. Sloan Foundation. \$750k \\
``MoBe DAC: A data coordinating center for the Sloan Indoor
Environment Metagenomic Project - Fungal resources''. \\
Role: PI.  Coordinated with F Meyer (U Chicago/ANL), R Knight (U Colorado), M Sogin (Marine Biological Lab).

\item [2014-2015] National Science Foundation. DBI-1429826. \$548k \\
``MRI: Acquisition of a Big Data Compute Cluster for Interdisciplinary
  Research''
Role: Co PI. PI T Girke. Co-Is J Bailey-Serres, M Allen, and S Lonardi (UCR)

\setlength{\cvlabelwidth}{18mm}

\begin{cvlistcompact}{\bf Service}
\item[{\bf University and Departmental}]
\item [2015--2016] Director \& Admissions Advisor, Microbiology Graduate Program
\item [2014--2015] Gradute Advisor, Microbiology Graduate Program
  \\  
\item[{\bf Editorial Boards}]
\item [2016--] Editorial Board, Current Opinion in Microbiology
\item [2015--] Associate Editor, Microbial Genomics
\item [2014--] Associate Editor, Fungal Genetics \& Biology
\item [2013,2015] Guest Associate Editor, PLoS Genetics
\item [2013] Guest Associate Editor, Mycologia
\item [2011--] Faculty Member in Microbial Genetics \& Genomics,
  Faculty of 1000
\item [2010--2015] Editorial Board, Eukaryotic Cell.
\item [2009--2016] Section Editor, PLoS One.
\item [2007--2016] Academic Editor, PLoS One.
\\
  
\item [{\bf Professional Service}]
\item [2018-2020] Co-Vice Chair (2018) and Co-Chair (2020) of Cellular and Molecular Fungal Biology, Gordon Research Conference
\item [2014--2018] Neurospora Policy Committee, Co-Organized 2016 Neurospora conference
\item [2013--2019] Fungal Genetics Policy Committee
\item [2012--2017] Scientific advisory board, Plant Microbe Interactions - DOE Science Focus Area, Oak Ridge National Laboratory
\item [2012--2018] Scientific advisory board, WormBase
\item [2012--2015] Scientific advisory board, EnsEMBL Genomes
\item [2010--2012] Councilor for Genetics \& Molecular Biology, Mycological Society of America
\item [2009--2010] Advisory Board for Genomic Encyclopedia of Fungi, Joint Genome Institute, US Department of Energy.
\item [2009--2010] Pan-Fungal Database Steering Committee for Burroughs Welcome Fund.
\item [2007--2009] Scientific advisory board for NSF funded Computer Science
  Education Revitalization project to PI Owen Astrachan, Duke
  University.
\item [2005--2008] Scientific advisory committee for Information Technology and
  Computing infrastructure for the National Center for Evolutionary
  Synthesis (NESCent).
\item [2005--2011] President and Board Member [2005--Present], Open Bioinformatics Foundation \url{http://www.open-bio.org/}
\item [2001--] Co-Project leader, BioPerl. \url{http://www.bioperl.org/}
%\item [2002-2008] Program Committee, Bioinformatics Open Source Conference; Chair (2002).
\\

\end{cvlistcompact}

\begin{cvlistcompact}{Membership in Professional Societies:}
\item [2002--] International Society for Computational Biology
\item [2004--] Society for Molecular Biology and Evolution
\item [2007--] American Society for Microbiology
\item [2004--] Genetics Society of America 
\item [2007--] Mycological Society of America 
\item [2001--] BioPerl developed. Co-Project leader (2001-2012).
\item [2002--] Open Bioinformatics Foundation 
%\item [2006--2007] Phyloinformatics working group, National Evolutionary
%  Synthesis Center, Durham, NC. 
\end{cvlistcompact}

%\begin{cvlistcompact}{Departmental Service:}
%\item [2010-2011] Admissions committee, Microbiology graduate program
%\item [2010-2011] Seminar committee, Plant Pathology \& Microbiology
%\item [2010-2011] Website committee, Microbiology Graduate program
%\item [2010-2011] Curriculum commitee, Genetic, Genomics, \&
%  Bioinformatics program
%\item [2010-2011] Social affairs committee, Plant Pathology \& Microbiology
%\item [2009-2010] Space and Infrastructure committee, Plant Pathology \& Microbiology
%\end{cvlistcompact}

\begin{cvlistcompact}{Graduate Students:}
\item [2009--13] PhD student, Divya Sain. Genetics, Genomics, \&
  Bioinformatics. Currently: Bioinformatics Scientist at Ambry Genetics.
\item [2010--12] MS student, Yi (Zoe) Zhu. Genetics, Genomics, \&
  Bioinformatics. Currently: Biostatistician at Biostatistical Consulting Inc.
\item [2014] MS student, Elizabeth Holmes, Plant Pathology \& Microbiology
\item [2010--14] PhD student, Yizhou Wang. Plant Biology. Currently:
  Research Bioinformatician at Cedars Sinai.
\item [2011--15] PhD student, Steven Ahrendt. Genetics, Genomics, \&
  Bioinformatics. Currently: Postdoc at UC Berkeley/LBNL \& DOE Joint
  Genome Institute.
\item [2015--] PhD Student, Sawyer Masonjones. Genetics, Genomics, \&
  Bioinformatics
\item [2015--] PhD Student, Nuttapom Pombubpa. Plant Pathology.
\item [2016--] PhD Student, Derreck Carter-House. Plant Pathology
\item [2016--] PhD Student, Jes\'{u}s Pe\~{n}a, Microbiology
\end{cvlistcompact}

\begin{cvlistcompact}{Postdoctoral Fellows:}
\item [2010--2011] John Abramyan, PhD. Currently: Postdoc at Univ of West
  Virgina
\item [2011--2014] Sofia Robb, PhD. Currently: Genomics Scientist at
  Stowers Institute.
\item [2012--2014] Brad Cavinder, PhD. Currently: Research Associate at Michigan
  State University
\item [2012--2015] Peng Liu, PhD. 
\item [2013--] Jinfeng Chen, PhD
\item [2013--2015] Ousmane Ciss\'{e}, PhD - Swiss National Science
  Foundation Fellow. Currently: Postdoctoral Fellow at NIH Clinical Center.
\item [2014--2015] Rodrigo Olarte. Currently: NSF Postdoctoral Fellow
  at Univ of Minnesota.
\end{cvlistcompact}

\begin{cvlistcompact}{Visitors:}
\item [2010--13 (4, 2-3 month vists)] Anastasia Gioti, PhD,
  Dept of Evolution Biology, Uppsala University, SWEDEN
\item [2010 (Spring)] Suzanne Joneson, PhD, Department of Biology, University of Idaho
\item [2011 (Spring)] Edgar Medina Tovar, MSc
  Mycology and Phytopathology Lab, Universidad de Los Andes, Bogota, COLOMBIA
\item [2012 (Summer)] Andrii Gryganski, PhD, Visiting Researcher, Duke University 
\item [2013--14] Venkatesh Moktali, PhD,
  FungiDB Project, Visiting Research Fellow, Oregon State University
\item [2014] Ra\'{u}l Castanera Andr\'{e}s, Visiting Graduate Student,
  Universidad P\'{u}blica de Navarra, Pamplona, SPAIN
\item [2015 (Spring)] Natalie Vande Pol, Visiting Graduate Student (Bonito Lab), Michigan State University
\item [2015--16] Zhinquan Song, Visiting Graduate Student (Guangyi
  Wang Lab), Tianjin University, CHINA
\item [2015 (Fall)] John Yinka Odebode, Visiting Graduate Student on a West
  African Research Assocation Fellowship, University of Lagos, NIGERIA.
\item [2015 (Fall)] Marco Marconi, Visiting Graduate Student,
    Universidad Polit\'{e}cnica de Madrid, Madrid, SPAIN
\item [2015--2016] Claudia Coleine, Visiting Graduate Student,
    Universit\'{a} degli Studi della Tuscia, Viterbo, ITALY
\end{cvlistcompact}

\begin{cvlistcompact}{Teaching:}

\item [2010,2012] BIO5C - Introductory Ecology \& Evolution 
\item [2011] BIO20 - The Dynamic Genome - Research module for \textit{Neurospora} research
\item [2011,2013] GEN240B - Tools for Bioinformatics and Genome Analysis
\item [2015] MCBL124 - Microbial Pathogenesis
\item [2011--] MCBL211 - Microbial Ecology
\item [2012-2015] MCBL202 - Microbial Pathogenesis \& Physiology
\item [2012-] GEN220 - Computational Analysis of High Throughput Biological Data \url{http://hyphaltip.github.io/GEN220_2015}
\item [2016--] BIO119 - Introduction to Genomics and Bioinformatics

\end{cvlistcompact}

\begin{cvlistcompact}{Undergraduate Researchers:}
\item[2010--] Sponsor for summer research students in MARCU, STEM, and CAMP
  programs at UCR.
\item [2010--2012] Jessica De Anda, UCR. STEM grant participant
  (2010); MARC USTAR student 2010-12. Current MS Student, Claremont College
\item [2010--2011] Annie Nguyen, UCR.
\item [2011--2012] Carlos Rojas Torres, UCR. CAMP (2011); lab
  researcher. Current: Gilead Pharmaceuticals.
\item [2011] Ramy Wissa, UCR. Pre-MARC USTAR Summer student.
\item [2011--2012] Lorena Rivera, UCR. Pre-MARC USTAR student (2011); lab
  researcher, CNAS Dean's Fellow Summer Undergraduate Research (Summer 2012)
\item [2012--2014] Erum Khan, UCR.
\item [2012--2014] Sapphire Ear, UCR. Current: CityYear and
  matriculating MD student (TBD).
\item [2012--2014] Megna Tiwari, UCR. Current: MS student at Cal
  State-Long Beach
\item [2013--2014] Dylan McVay, UCR.
\item [2013--2016] Na Jeong, UCR, Summer RISE Scholar (2013) and lab researcher
\item [2014] Spencer Swansen, Summer NSF REU student (Seattle Pacific University)
\item [2015--2016] Justin Shen, UCR.
\item [2015--2016] Serena Choi, UCR.
\item [2015--] Dillon McDonald, UCR Summer HSI-STEM (2015) and lab researcher
\item [2015] Christina Uriarte, UCR. Pre-MARC USTAR student.
\item [2015--] Jericho Ortanez, UCR.
\item [2015--2016] Leandra Ibrahim, UCR.
\item [2015--] Deane Kim, UCR.
\item [2016--] Georgiy Smirnov, UCR.
\item [2016--] Meng (Josh) Chung, UCR.
  
\end{cvlistcompact}

\begin{cvlistcompact}{Dissertation and thesis committees:}
\item [2011] Sourav Roy, PhD, GGB
\item Yi Zhou, MS, GGB $\star$
\item [2012] Andrew Defries, PhD, Plant Sciences
\item [2013] Gilbert Uribe, MS, Plant Pathology
\item Divya Sain, PhD, GGB $\star$
\item [2014] Yizhou Wang, PhD, Plant Sciences $\star$
\item Zhigang Wu, PhD, GGB
\item [2015] Presha Shah, PhD, Biochemistry
\item Ming Wang, PhD, Plant Pathology
\item Steven Ahrendt, PhD, GGB $\star$
\item Ilva Cabrera, PhD, GGB
\item Jinfeng Lu, PhD, GGB
\item James Ricci, MS, Entomology
\item [2016] Ryan Arvidson, PhD, Biochemistry
\item Francis Na, MS, Microbiology
\item Jishu Ha, PhD, GGB
\item Arit Gosh, PhD, GGB
\item [ongoing] Kelsey Gano, Microbiology
\item Kun Liu, Plant Biology
\item Raissa Green, GGB
\item Amelia Lindsey, Entomology
\item Patrick Schriener, GGB
\item Cynthia Dick, EEOB
\item Eric Gordon, Entomology
\item Eric Smith, GGB
\item Dereck O'Meara, EEOB
\item Yi Zhai, CMDB
\item Andrea Vu, Plant Pathology
\item Steven Bolaris, GGB
\item Dinusha Maheepala Mudalige, Plant Biology
\item Nuttapon Pombubpa, Plant Pathology $\star$
\item Derreck Carter-House, Plant Pathology $\star$
\item Sawyer Masonjones, GGB $\star$
\item Jes\'{u}s Pe\~{n}a, Microbiology $\star$
\item Nathan Robinett, Joint Doctoral Program in Evolutionary Biology, SDSU-UCR
\item Katherine Picard, UPGG - Duke University
\item Edgar Medina, UPGG - Duke University
\item Lluvia Vargas, Microbiolog\'{i}a - CICESE, MEXICO
\item Dan Vanderpool, Biology, University of Montana
\end{cvlistcompact}

\end{cvlistcompact}
% cvlist items can take dates as a parameter.

\setlength{\cvlabelwidth}{7mm}
\begin{cvlistcompact}{\bf Invited Seminars and conference presentations (2015--Present)}
\item [2016] $\cdot$  \textit{Fungal population genomics of emerging
  diseases in plants, frogs, and people} \\
  Mycological Society of America 2016 Meeting. Berkeley, CA. 
  \item $\cdot$     \textit{Genomes of early diverging fungi enable
    new insights into the evolution of complexity in fungi} \\
    CIFAR Integrated Microbial Biodiversity Program/Review,  Toronto, ON, CANADA.
  \item $\cdot$     \textit{Genome evolution in early diverging fungi from the 1000 fungal genomes perspective} \\
    Plenary Speaker. 13th European Fungal Genetics Conference.
    Paris, France. 
  \item $\cdot$ \textit{A Novel DNA transposon is recognized and 
    silenced by Meiotic Silencing by small RNAs} \\
    Neurospora Conference. Asilomar Conference Center, Pacific
    Grove, CA.
  \item $\cdot$ \textit{Insights from the 1000
    Fungal Genomes project: Comparative biology and phylogeny} \\
    University Program in Genetics \& Genomics. Duke University, Durham, NC. 
  \item $\cdot$ \textit{Genomics of early diverging fungi for phylogeny and
  comparative biology} \\
    Dept of Plant Pathology. University of California, Davis,
    CA. 
  \item $\cdot$  \textit{Insights from the
    1000 Fungal Genomes project: Comparative biology and phylogeny} \\
    University of Exeter. United Kingdom.   
\item [2015] $\cdot$  \textit{Evolutionary Genomics of Early Branches
  of the Fungal Tree of Life} \\
  Exploring the genomic complexity and diversity of
  eukaryotes. EMBO Conference, San Feliu de Guixols, SPAIN.\\

\item $\cdot$     \textit{Comparing molecular and
  morphological fungal evolution through studies of fungal genomes} \\
  XI CONGRESO NATIONAL DE MICOLOGIA, Sociedad Mexicana de
  Micologia. Merida, Yucatan, MEXICO. 
  \item $\cdot$   \textit{Evolution of complexity in fungi from evolutionary
    genomics of early diverging lineage} \\
  School of Plant Sciences, University of Arizona, Tucson,
    AZ. 
  \item $\cdot$ \textit{Evolutionary genomics of early branches of the
    fungal tree \& the ZyGoLife project} \\
    Eighth International Conference on Mycorrhiza.
    Flagstaff, AZ. 
  \item $\cdot$ \textit{Evolutionary genomics of early branches
    of the fungal tree: A view from the 1000 Fungal Genomes Project
    and ZyGoLife Project} \\
    Mycological Society of America 2015 Meeting. Edmonton, AB, CANADA. 
  \item $\cdot$  \textit{Evolutionary genomics of early
    branches of the fungal tree: The 1000 Fungal Genomes Project} \\
    Society for Molecular Biology \& Evolution 2015. Vienna, Austria.
  \item $\cdot$  \textit{Evolutionary and functional genomics in early
    diverging fungi} \\
    Bioinformatics Seminar series. University of California, Los Angeles.
  \item $\cdot$  \textit{Evolutionary and functional genomics in early
    diverging fungi} \\
    University of California, Merced, CA. 
  \item $\cdot$   \textit{Phylogenomics of the Zygomycete lineages: Exploring
    phylogeny and genome evolution} \\
    28th Fungal Genetics Conference. Asilomar Conference Center,
    Pacific Grove, CA. 
  \item $\cdot$  \textit{Evolutionary and functional genomics in early
    diverging fungi} \\
    Center for Genome Research and Biocomputing Seminar. Oregon
    State University, Corvallis, OR.
  \item $\cdot$ \textit{Clues to multicellular evolution of fungi from
    comparative genomics \& studies of early diverging fungi} \\
    Microbiology and Molecular Genetics. Oklahoma State University, Stillwater, OK. \\
    
%  \item [2014] $\cdot$ Stazione Zoologica Anton Dohrn. Naples,
%    ITALY. \textit{Evolutionary genomics and the origins of multicellular forms in filamentous fungi}
%
%\item [2011] $\cdot$ Center for Comparative Genomics \& Bioinformatics, Penn State University, State College, PA.
%\item $\cdot$ Department of Biology, San Diego State University, San Diego, CA
%\item $\cdot$ Bio-IT Cloud Summit, La Jolla, CA
%\item $\cdot$ Molecular Mycology Course, Marine Biological Lab, Woods Hole, MA
%\item $\cdot$ Mycological Society of America, Fairbanks, AK
%\item $\cdot$ Workshop in Comparative Genomics, Ft Collins, CO
%\item $\cdot$ $8^{th}$ Internation Cryptococcus and Cryptococcosis Conference, Charleston, SC
%\item $\cdot$ Symbiosis Workshop, Yosemite NP, CA
%\item $\cdot$ $26^{th}$ Fungal Genetics Conference, Asilomar Conference Center, Pacific Grove, CA. %(Session Chair: Comparative and Functional Genomics)
%\item $\cdot$ University of California-Davis, Department of
%  Plant Pathology, Davis, CA
%\item [2010] $\cdot$ National University of Ireland, Maynooth, Department of Biology, Maynooth, Ireland
%\item $\cdot$ Basidiomycete Genomics workshop, Joint Genome Institute User
%  meeting, Walnut Creek, CA
%\item $\cdot$ University of California-Riverside, GGB Seminar Series, Riverside, CA.
%\item $\cdot$ 2010 Neurospora Conference, Asilomar Conference Center, Pacific Grove, CA
%\item $\cdot$ PBoFF Symposium, Texas A \& M University, College Station, TX.
%\item $\cdot$ Cellular and Molecular Biology of Fungi, Gordon Research
%  Conference, Holderness, NH.
%\item $\cdot$ Mycological Society of America, Lexington, KY
%\item $\cdot$ $9^{th}$ International Mycological Congress, Scotland, UK
%\item [2009] $\cdot$ University of California-Riverside, Department of Computer Science, Riverside, CA.
%\item $\cdot$ University of California-Los Angeles, MSRI Bioinformatics Series,
%  Los Angeles, CA.
%\item $\cdot$ Comparative Genomics of Eukaryotic Microorganisms, EMBO
%  Conference, San Feliu de Guixols, Spain. 
%\item $\cdot$ University of Idaho, Initative for Bioinformatics and
%  Evolutionary Studies, Moscow, ID.
%\item $\cdot$ Molecular Mycology Course, Marine Biological Lab,
%  Woods Hole, MA.
%\item $\cdot$ Mycological Society of America, Snowbird, UT.
%\item $\cdot$ Eccles Institute, University of Utah, Deptartment of Human Genetics, Salt Lake City, UT.
%\item $\cdot$ Bioinformatics Symposium \& Workshop, Oregon State University,
%  Corvallis, OR. 
%\item $\cdot$ $25^{th}$ Fungal Genetics Conference, Asilomar Conference
%  Center, Pacific Grove, CA. %(Session Chair: Evolutionary Genetics \& Genomics) 
%\item $\cdot$ University of Arizona, Genomics IGERT Program, Tucson, AZ.
%\item $\cdot$ Michigan State University, Pythium Genome Workshop, East
%  Lansing, MI.
%\item $\cdot$ Cornell University, Department of Plant Pathology, Ithaca, NY.
%\item $\cdot$ Graduate Research School in Genomic Ecology, Winter meeting,
%  Lund University, Lund, Sweden. 
\end{cvlistcompact}


\end{cv}
\end{document}
