\documentclass[10pt]{article}
\usepackage{refcount}
\usepackage{charter}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage[resetlabels]{multibib}
\usepackage[ManyBibs,LabelsAligned]{currvita}
\usepackage{ifpdf}
\usepackage{denselists}
%\usepackage{revnum}

\ifpdf
  \usepackage[pdftex,pdfpagelabels=false]{hyperref}
\else
  \usepackage[hypertex,pdfpagelabels=false]{hyperref}
\fi
\usepackage{setspace} 
\hypersetup{
  pdfauthor={Jason E Stajich}
  pdftitle={CV for Jason Stajich}
  pdfsubject={Detailed CV for Jason},
  urlcolor=blue,
}

% Initialize each paper type for which you need a bibliography.
\newcites{journalFivePage}{Selected Peer Reviewed Publications}

\makeatletter
\long\def\thebibliography#1{%
  \section*{\refname}%
  \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}
  \settowidth{\dimen0}{\@biblabel{#1}}%
  \setlength{\dimen2}{\dimen0}%
  \addtolength{\dimen2}{\labelsep}
  \sloppy
  \clubpenalty 4000 
  \@clubpenalty 
  \clubpenalty 
  \widowpenalty 4000
  \sfcode `\.\@m
  \renewcommand{\labelenumi}{\@biblabel{\theenumi}} % labels like [3], [2], [1]
  \begin{etaremune}[labelwidth=\dimen0,leftmargin=\dimen2]\@openbib@code
}
\def\endthebibliography{\end{etaremune}}
\def\@bibitem#1{%
  \item \if@filesw\immediate\write\@auxout{\string\bibcite{#1}{\the\value{enumi}}}\fi\ignorespaces
}
\makeatother

% Specify the bibtex style that you want for each paper type
\bibliographystyle{nih}
\bibliographystylejournalFivePage{nih}

\newlength{\oldcvlabelwidth}
\renewcommand*{\cvbibname}{}

\begin{document}

% This is what will appear at the very top of your CV.
\begin{cv}{\centerline{Jason E. Stajich}}

% Items have more vertical space between them than line breaks.
% Note: if you want a linebreak after each cvlist title, you can do:
% \begin{cvlist}{Title \hspace{3in}}

\setlength{\cvlabelwidth}{18mm}
\begin{cvlistcompact}{Contact}
\item{Department of Plant Pathology \& Microbiology, Institute for
  Integrative Genome Biology, \\
  University of California, Riverside, CA 92521}
  \item{ \textbf{Telephone:} +1 951-827-2363 \textbf{Email:}
    jason.stajich@ucr.edu \\
    \textbf{Web:} \url{http://lab.stajich.org/} {\tt @stajichlab @hyphaltip}}
\end{cvlistcompact}

\begin{cvlistcompact}{\bf Education}
\item [2006--2009] Postdoctoral training, University of California, Berkeley, CA. Mentor: Dr. John W Taylor
\item [2001--2006] Ph.D. in Genetics and Genomics, Duke University, Durham, NC. Advisor: Dr. Fred S Dietrich
\item [1995--1999] B.S. in Computer Science, Duke University, Durham, NC
\end{cvlistcompact}

\begin{cvlistcompact}{\bf Academic appointments:}
\item [2014--] Associate Professor (with tenure)
  \\ Dept of Plant Pathology \& Microbiology. University of California Riverside
\item [2009--2014] Assistant Professor
  \\ Dept of Plant Pathology \& Microbiology. University of California Riverside.
\item [2006--2009] Postdoctoral Research Fellow. Miller Institute for Basic Research. \\
  Dept of Plant and Microbial Biology, University of California
  Berkeley.
\end{cvlistcompact}

\begin{cvlistcompact}{Honors and Awards:}
\item [2015] Kavli Fellow, Kavli Frontiers of Science
\item [2014] C. J. Alexopoulos Prize, Mycological Society for America
\item [2006--2009] Miller Institute for Basic Research in Science,
  Postdoctoral Research Fellowship
\item [2003--2006] National Science Foundation, Graduate Research Fellowship
\end{cvlistcompact}

% These commands will make our papers be indented after the first line
% to make the author's name stand out more.  Also, we reduce the
% indentation of the paper type titles (e.g., Journal Papers,
% Conference Paper) compared to regular cvlist items.
\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\renewcommand*{\bibindent}{1.5em}
% Do bibaddtoleftmargin instead of biblabelsep if you're
% not using manybib Or open bib
%\renewcommand*{\bibaddtoleftmargin}{1.5em}
\renewcommand*{\biblabelsep}{1.5em}

% To update, before doing latexmk, run:
% bibtex journal
% bibtex refpaper
% bibtex unrefpaper
% bibtex techreport

\makeatletter
\def\thebibliography#1{\list
{\arabic{enumiv}.}{\settowidth\labelwidth{[#1]}\leftmargin\labelwidth
\advance\leftmargin\labelsep
\usecounter{enumiv}}
\def\newblock{\hskip .11em plus .33em minus .07em}
\sloppy\clubpenalty4000\widowpenalty4000
\sfcode`\.=1000\relax
}
\let\endthebibliography=\endlist
\makeatother

\begin{cvlist}{Selected Publications (out of 90): (Listed in reverse chronological order.)}
\item 
  \def\mybibitem#1{\item}
  \nocitejournalFivePage{Ahrendt2017}
  \nocitejournalFivePage{Nguyen2017}
  \nocitejournalFivePage{Chen2017}
  \nocitejournalFivePage{Spatafora2016}
  \nocitejournalFivePage{Castanera2016}
  \nocitejournalFivePage{deMan2016}
  \nocitejournalFivePage{Wang2015}
  \nocitejournalFivePage{Liu2015}
  \nocitejournalFivePage{Melida2015}
\nocitejournalFivePage{Inglis2014}
\nocitejournalFivePage{Gioti2013b}
\nocitejournalFivePage{James2013}
\nocitejournalFivePage{Rosenblum2013}
\nocitejournalFivePage{Robb2013}
\nocitejournalFivePage{Gioti2013a}
\nocitejournalFivePage{Abramyan2012}
\nocitejournalFivePage{Stajich2012}
\nocitejournalFivePage{Joneson2011}
\nocitejournalFivePage{Ellison2011}
\nocitejournalFivePage{Stajich2010}
\nocitejournalFivePage{Nowrousian2010}
\nocitejournalFivePage{Sharpton2009}
\nocitejournalFivePage{Martin2008}
\nocitejournalFivePage{Stajich2007a}
\nocitejournalFivePage{Fitzpatrick2006}
\nocitejournalFivePage{James2006}
\nocitejournalFivePage{Kaemper2006}
\nocitejournalFivePage{Stajich2006a}
\nocitejournalFivePage{Fraser2005}
\nocitejournalFivePage{Stein2002}
\nocitejournalFivePage{Stajich2002}
\bibliographyjournalFivePage{stajichpubs}
  
\begin{cvlistcompact}{\bf Software and other Products}
  \item $\cdot$ BioPerl - \url{http://bioperl.org} - Core developer
\item  $\cdot$ Github projects \url{http://github.com/stajichlab},
  \url{http://github.com/hyphaltip}, \url{http://github.com/1KFG} - 1000 Fungal
   genomes, \url{http://github.com/zygolife} ZyGoLife Phylogenomics
\item $\cdot$ ``The Hyphal Tip'': \url{http://fungalgenomes.org/blog}
  - I write about fungal genomics
  Tip''$\cdot$ Comparative geomomics website \& Database (Collaboration): \url{http://fungidb.org}
\end{cvlistcompact}


\end{cvlist}
% Reset the label indentation
\setlength{\cvlabelwidth}{24mm}

%\begin{cvlist}{Employment}
%	\item[Summer 2002] Visiting Researcher, Lincoln D Stein laboratory \\
%          Cold Spring Harbor Laboratories, Cold Spring Harbor, NY
%	\item[1999--2001] Analyst/Programmer, Center for Human
%          Genetics \\
%          Duke University Medical Center, Durham, NC          
%\end{cvlist}

\begin{cvlistcompact}{\bf Grant Support:}
\item [{\bf Ongoing support}]

\item [2011-2016] W.M. Keck Foundation. (\$1M) ''New Active
  Transposable Elements for Mosquito Genetics.'' \\
Role: Co-I. PI: SR Wessler (UC Riverside). Co-I: P Atkinson (UC Riverside). 

\item [2011-2017] NSF IOS-1027542. (\$4.9M) ``CPGS: Genome-wide impact of \textit{mPing} transposition on rice phenotypic diversity.'' \\
Role: Co-I. PI: SR Wessler (UC Riverside). Co-I: T Brutnell, Q Sun. 

\item [2014-2017] NIH 1-R01-GM108492-01. (\$1.5M) ``Dynamics of bacterial-fungal interactions in chronic lung infections'' \\
Role: Co-I. PI: D Hogan (Dartmouth)

\item [2015-2018] NSF GO Life DEB-1441715. (\$714k;\$2.5M total award) ``The Zygomycetes Genealogy of Life (ZyGoLife)- the conundrum of Kingdom Fungi'' \\
  Role: PI. 3 other PIs and ~12 collaborating labs. \url{http://zygolife.org} 

\item [2016-2019] NSF DEB-1557110. (\$317k;\$709k total award) ``Phylogenomics and evolutionary history of the anaerobic fungal group, Neocallimastigomycota'' \\
Role: PI. Collaborative award with PI: Noha Youssef \& Mostafa Elshahed (Oklahoma State)

\item [2017-2020] UCalifornia Office President. (\$105k;\$1.7M total award) ``UC Valley Fever Research Initiative'' \\
Role: Co-PI. Collaborative award with PI: Anita Sil (UCSF)

\item [{\bf Completed support}]

\item [2010-2013] Burroughs Wellcome Fund. (\$500k) ``FungiDB: A Pan Fungal Genome Database''. \textbf{Role:} Co-I. PI: DS Roos (U Pennsylvania)

\item [2013-2014] NIH 1-R03-AI105636-01. (\$168k) ``Annotation of
  \textit{Cryptococcus} genomes by comprehensive curation of published
  literature.'' \textbf{Role:} PI. Co-I G Sherlock (Stanford)

  \item [2011-2014] Alfred P. Sloan Foundation. (\$750k) ``MoBe DAC: A
    data coordinating center for the Sloan Indoor Environment
    Metagenomic Project - Fungal resources''. \textbf{Role:} PI.
    Coordinated project with grantees Folker Meyer, Rob Knight, Mitchell Sogin.

\setlength{\cvlabelwidth}{18mm}
  
\item [{\bf Professional Service}]
\item [2018-2020] Co-Vice Chair (2018) and Co-Chair (2020) of Cellular and Molecular Fungal Biology, Gordon Research Conference
\item [2014--2018] Neurospora Policy Committee, Co-Organized 2016 Neurospora conference
\item [2013--2019] Fungal Genetics Policy Committee
\item [2012--2018] Scientific advisory board (SAB): WormBase
\item [2012--2017] SAB: Plant Microbe Interactions - DOE Science Focus Area, Oak Ridge National Laboratory
\item [2012--2017] SAB: EnsEMBL Genomes
\item [2010--2012] Councilor (Genetics \& Molecular Biology) Mycological Society of America
\item [2009--2010] Advisory Board, Genomic Encyclopedia of Fungi, Joint Genome Institute
\item [2005--2013] President (2005-2011), Board Member [2005--2013], Open Bioinformatics Foundation
\item [2001--] Co-Project leader, BioPerl. \url{http://www.bioperl.org/}
%\item [2002-2008] Program Committee, Bioinformatics Open Source Conference; Chair (2002).
\\

\end{cvlistcompact}


\setlength{\cvlabelwidth}{8mm}
\begin{cvlistcompact}{\bf Invited Seminars and conference presentations (2015--Present)}
\item [2017] $\cdot$ 29$^{th}$ Pleneary lecturer. Fungal Genetics,
  Asilomar Conference Grounds, Pacific Grove, CA
  \item $\cdot$ Keynote, Oomycete Molecular Genetics Network. Asilomar Conference Grounds, Pacific Grove, CA
\item [2016] $\cdot$
%  \textit{Fungal population genomics of emerging
%  diseases in plants, frogs, and people} \\
  Mycological Society of America 2016 Meeting. Berkeley, CA. 
\item $\cdot$
  %\textit{Genomes of early diverging fungi enable
%    new insights into the evolution of complexity in fungi} \\
    CIFAR Integrated Microbial Biodiversity Program. Toronto, ON, CANADA.
  \item $\cdot$   %  \textit{Genome evolution in early diverging fungi from the 1000 fungal genomes perspective} \\
    13th European Fungal Genetics Conference.
    Paris, France.  {\it Plenary Speaker}
  \item $\cdot$ % \textit{A Novel DNA transposon is recognized and 
%    silenced by Meiotic Silencing by small RNAs} \\
    Neurospora Conference. Asilomar Conference Center, Pacific
    Grove, CA.
\item [2015] $\cdot$ % \textit{Evolutionary Genomics of Early Branches
%  of the Fungal Tree of Life} \\
  Exploring the genomic complexity and diversity of
  eukaryotes. EMBO Conference, San Feliu de Guixols, SPAIN. 
\item $\cdot$   %  \textit{Comparing molecular and
%  morphological fungal evolution through studies of fungal genomes} \\
  XI CONGRESO NATIONAL DE MICOLOGIA, Sociedad Mexicana de
  Micologia. Merida, Yucatan, MEXICO. {\it Plenary Speaker}
  \item $\cdot$ % \textit{Evolutionary genomics of early branches of the
%    fungal tree \& the ZyGoLife project} \\
    Eighth International Conference on Mycorrhiza.
    Flagstaff, AZ. 
  \item $\cdot$ %\textit{Evolutionary genomics of early branches
    %of the fungal tree: A view from the 1000 Fungal Genomes Project
   % and ZyGoLife Project} \\
    Mycological Society of America 2015 Meeting. Edmonton, AB, CANADA. 
  \item $\cdot$  %\textit{Evolutionary genomics of early
   % branches of the fungal tree: The 1000 Fungal Genomes Project} \\
    Society for Molecular Biology \& Evolution 2015. Vienna, Austria.
\end{cvlistcompact}


\end{cv}
\end{document}
